ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-06-09 paper/wish/wsc15paper.tex
last
montreal

\author{
	Saul Toscano-Palmerin\\ 
    	Peter I. Frazier\\[12pt]
	Cornell University \\
	257 Rhodes Hall \\
	206 Rhodes Hall \\
	Ithaca, NY 14853, USA\\
}

@@

This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm can be generalized to the continuous case (see  \citeN{Frazier:BIZ}).

>>>>

\author{
	Saul Toscano-Palmerin\\ 
    	Peter I. Frazier\\[12pt]
	Cornell University \\
	257 Rhodes Hall \\
	232 Rhodes Hall \\
	Ithaca, NY 14853, USA\\
}

@@

This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that $B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm can be generalized to the continuous case (see  \citeN{Frazier:BIZ}).
